Apples and Oranges in Adolescent Depression Treatments.

### 2024-01-04 apples_and_oranges.qmd
Some very minor changes

@@

# also rename active_type to treatment for the merge below.
turn_long_active_type <- rename(turn_long_active_type,treatment = descr_active,
                                baseline_n = baseline_n_active)

>>>>

df_appl_v_orange <- df_appl_v_orange %>% 
  mutate(descr_active = if_else(is.na(descr_active ), active_type , descr_active ))

@@

# also rename active_type to treatment for the merge below.
turn_long_active_type <- rename(turn_long_active_type, treatment = descr_active,
                                baseline_n = baseline_n_active)
